Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex
Currency section complete

As mentioned in section \ref{sec:related}, many other applications failed to create a captivating game for children. We wanted to have an application that children would see less as homework, and more of a game. This was the underlying motivation for making {\em Kimbee} a game. In order for a game to be immersive, a sense of progression must be present \cite{Ermi:Gameplay}.

>>>>

As mentioned in section \ref{sec:related}, many other applications failed to create a captivating game for children. We wanted to have an application that children would see less as homework, and more of a game. This was the underlying motivation for making {\em Kimbee} a game. In order for a game to be immersive, a sense of progression must be present \cite{Ermi:Gameplay}. We were able to create this using the honey collected as a currency. We also added the dynamic scoring of the honey, with the collection of the pots and completion of the challenges.

Many therapists currently use operant conditioning as a reward system \cite{Kreider:Intro}. For example, Mr. Kreider rewards children with small toys after they do well on a set of phrases. A reward system could be implemented where the currency is the honey from {\em Kimbee}. This would encourage students to play the game outside of the therapy sessions and motivate them to improve over time. As this was only a quarter long project, this is left as future work.
